\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic} 
\moderncvcolor{green}
\setlength{\hintscolumnwidth}{2cm} 
\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{helvet}
\usepackage[french]{babel}
\name{Mickaël}{Moreau}
\title{Hardware verification Engineer} 
\address{50 lotissement Rivoire de la Dame}{38360 Sassenage, France}
\phone[mobile]{06~88~33~15~88}
%\phone[fixed]{01~01~88~33~55}
%\phone[fax]{02~11~22~33~44}
\email{mickael.moreau@gmail.com}
%\homepage{www.pierredurand.com}
%\social[linkedin]{pierre.durand}
%\social[twitter]{pierre.durand}
%\social[github]{pierre.durand}
\extrainfo{42 years old - Married - 3 children}
%\photo[64pt][0.4pt]{maphoto}
%\quote{Ingénieur en micro-électronique}
\begin{document}
\makecvtitle
\section{Relevant experience}
\cventry{2014--2016}{Verification engineer for IP Graphic}{STMicroelectronics}{Grenoble}{}%
{%
\begin{itemize}%
\item Upgrade a legacy environement based on Specman  (ex : Git, Jenkins, regression tool,...).
\item Develop a scenario generator  based on  C++.
\item Develop LLD (Low-Level Driver) based on C.
\item Evaluate and deploy C/C++ static analyzer.
\end{itemize}}

\cventry{2008--2014}{Central verification engineer}{STMicroelectronics}{Grenoble}{}%
{%
\begin{itemize}%
\item Develop, evaluate and deploy of verification tools :
 \begin{itemize}%
 \item \textit{Verification-Cockpit} : generic environement for verification (Perl).
\item MySQL database to record the history of the verification.
\item Report to follow the verification evolution.
\item Verification environement for the next generation of SOC.
\item Integration of formal qualification.
\end{itemize}
\item Manage simulators benchmark (RTL and Gates).
\end{itemize}}

\cventry{2006--2008}{CAD support engineer}{STMicroelectronics}{Grenoble}{}%
{%
\begin{itemize}%
\item Softwares and licenses installation.
\item Support of verification tools and simulators.
\item Developpement and support of CAD navigation tools.
\end{itemize}}

\cventry{1999--2006}{Electical Failure analysis engineer }{STMicroelectronics}{Grenoble}{}{%
\begin{itemize}
\item Develop and deploy of new localisation technics thanks EDA tools.
\item Manage CAD navigation tools.
\end{itemize}}

\section{Education}
\cventry{1995--1998}{\'Ecole d'ingénieur}{Supélec}{Rennes}{\textit{Options micro-électronique}}{}
\cventry{1991--1995}{\'Ecole préparatoire TA}{Lycée Léonce Vieljeux}{La Rochelle}{}{}
\cventry{1989--1991}{BAC F2 électronique}{Lycée Louis Armand}{Poitiers}{}{}
\cventry{1987--1989}{BEP électronique}{Lycée Edouard Branly}{Châtellerault}{}{}

\section{Skills}
\cvdoubleitem{Languages}{Perl, Tcl, Java, C/C++, SQL}{HDL}{VHDL, Verilog, e, SystemC}
\cvdoubleitem{Simulator}{NCsim, VCS, Questa, Eldo}{Verification}{Specman, Certitude, vManager}
\cvdoubleitem{ATPG}{TetraMax}{LVS}{Calibre}
\cvdoubleitem{BI}{BIRT, QlikView}{Others}{Git, Subversion, Jenkins}

\section{Conference}
\cventry{2012}{DAC}{\fontsize{10}{11}\selectfont "Integration of Enterprise Manager SQL database in Verification-Cockpit"}{Poster}{}{}
\cventry{2009}{DVCON}{\fontsize{10}{11}\selectfont "Unified Formal and Dynamic Verification Closure: Can Mutations Bridge the Gap?"}{Papier}{}{}

\section{Hobbies}
\cvdoubleitem{Culture}{Movies, Series, Electronic music}{Computer}{Video games, Coding games}
\cvitem{Sport}{Cycling}

\end{document}
